
\documentclass[letterpaper,11pt]{article}

\usepackage[utf8]{inputenc}
\usepackage[dvipsnames]{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{graphicx}
\usepackage[left=.95in, right=1.1in, bottom=.9in, includehead, headheight=0pt]{geometry}
\usepackage[
    colorlinks=true,
    urlcolor=black,
    linkcolor=black,
    citecolor=black,
    pdfborder={0 0 0}
]{hyperref}

\urlstyle{same}
\pagestyle{fancy}
\fancyhf{}x
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\setlength{\headsep}{0.2in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in}
\addtolength{\textheight}{1.0in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-5pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-8pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.12in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-7pt}}

%-------------------------------------------
\begin{document}

% ---------- Header (self-contained) ----------
\begin{flushleft}
{\huge\bfseries Owen Fisher}\\[-0.1em]        % bigger name + tighter gap
\href{https://owen-portfolio-git-main-owens-projects-e5b63a60.vercel.app/}{Portfolio}\,$|$\,%
\href{https://www.linkedin.com/in/fisherowen}{LinkedIn}\,$|$\,%
\href{https://github.com/obro79}{GitHub}\,$|$\,%
\href{mailto:owenfisher46@gmail.com}{OwenFisher46@gmail.com}\,$|$\,778--700--5680
\end{flushleft}
\vspace{-1.5em}                               % pull next section up a bit

% ------------------- Education -------------------
\section{\textcolor{Plum}{Education}}
\resumeSubHeadingListStart
  \resumeSubheading
  {The University of British Columbia}{\textbf{Vancouver, BC}}
  {\textbf{B.Sc., Math, Minor Computer Science} (GPA: 3.7/4.0)}{Expected Graduation: May 2027}
  \resumeItemListStart
      \resumeItem{Coursework: Software Engineering, Probability, DSA, Stochastic Processes, Machine Learning}
  \resumeItemListEnd
\resumeSubHeadingListEnd

% ------------------- Technical Skills -------------------
\section{\textcolor{Plum}{Technical Skills}}
\textbf{Languages}: Python (NumPy, Pandas, Matplotlib), C++, Java, R, PostgreSQL, MATLAB, TypeScript\\
\textbf{Tools \& Testing}: Git, CI/CD --- GitHub Actions \& Vercel, PyTest, Cypress

% ------------------- Experience -------------------
\vspace{-0.5em}
\section{\textcolor{Plum}{Experience}}
\vspace{0.25em }
\resumeSubHeadingListStart

  \resumeSubheading
  {Quantitative Developer}{Vancouver, BC}
  {RBC Global Asset Management}{Sept. 2025 -- Dec. 2025}
  \resumeItemListStart
    \resumeItem{Will re-engineer MATLAB pricing-risk engine to modular Python + Dask on Helios---forecast for 70\% faster valuations and 50\% shorter releases via CI/CD.}
  \resumeItemListEnd

  \resumeSubheading
  {Quantitative Developer}{Vancouver, BC}
  {Quantico Research}{Jan. 2025 -- May 2025}
  \resumeItemListStart
    \resumeItem{Built real‑time pipelines to ingest \& clean seismic streams at sub‑200ms latency.}
    \resumeItem{Applied \textbf{HMM} for real‑time seismic risk adjustment, improving internal alert thresholds.}
    \resumeItem{Automated walk‑forward validation and stress tests in CI/CD for reproducible model releases.}
  \resumeItemListEnd

  \resumeSubheading
  {Frontend Engineer}{Vancouver, BC}
  {UBC Actuarial Science Club}{May. 2025 -- Present}
  \resumeItemListStart
      \resumeItem{Spearheaded website build using Next.js, React \& Tailwind CSS, boosting club engagement +200\%.}
      \resumeItem{Built interactive course planning tool serving 150+ students, streamlining semester planning workflows.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

% ------------------- Technical Projects -------------------
\section{\textcolor{Plum}{Technical Projects}}
\resumeSubHeadingListStart

  \resumeProjectHeading
  {\textbf{Bayesian Gaussian Process Modeling of SPY Implied Volatility}$|$\href{https://www.notion.so/Bayesion-Non-Parametric-Model-Paper-206b9c270459808bb413dadf3f9126eb}{\underline{Paper}}$|$
  \emph{Stan, R, Python}}{}
  \resumeItemListStart
      \resumeItem{Built Bayesian GP model in Stan for SPY IV surfaces with linear mean and Matérn 3/2 kernel.}
      \resumeItem{Optimized MCMC via blocked Gibbs \& Elliptical Slice Sampling with $k=20$, reducing complexity to $\mathcal{O}(Nk^2)$.}
      \resumeItem{Generated out-of-sample forecasts with $<4\%$ error, enhancing option pricing and risk management.}
  \resumeItemListEnd

  \resumeProjectHeading
  {\textbf{Orderbook Engine} {\underline{Github}}$|$ \emph{C++, STL}}{}
  \resumeItemListStart
    \resumeItem{Built an in‑memory limit order book supporting GTC \& FAK orders with $O(\log n)$ complexity.}
    \resumeItem{Implemented real‑time bid/ask aggregation using C++17 lambdas and STL algorithms for analytics.}
    \resumeItem{Created unit‑test suite and VS integration, ensuring robust order‑matching logic.}
  \resumeItemListEnd

  \resumeProjectHeading
  {\textbf{Reinforcement Learning Trading Strategy} \href{https://github.com/obro79/RL-trading-strat?tab=readme-ov-file}{\underline{Github}}$|$\href{https://rl-trading-strat.streamlit.app}{\underline{Live Demo}}$|$\emph{Python, PyTorch, Gymnasium}}{}
  \resumeItemListStart
     \resumeItem{Trained PPO and A2C agents in a custom Gym trading environment for transaction cost modeling.}
     \resumeItem{Built a data pipeline using yfinance and pandas to engineer OHLCV features and indicators for agent inputs.}
     \resumeItem{Developed a Streamlit dashboard for visualization of agent performance, indicator trends, and backtest metrics.}
  \resumeItemListEnd

  \resumeProjectHeading
  {\textbf{Stock Price Forecasting with XGBoost}
  \href{https://github.com/obro79/arima}{\underline{Github}}$|$\emph{Python, NumPy, Scikit-Learn, Matplotlib}}{}
  \resumeItemListStart
      \resumeItem{Built \textbf{XGBoost} model on yfinance data with engineered NumPy indicators; achieved MAE 1.5 and MRE 1\%.}
      \resumeItem{Backtested signals over 20 years to compare ROI vs.\ buy-and-hold, guiding model refinements.}
      \resumeItem{Created Streamlit dashboard for prediction visualization, indicator plots, and strategy metrics.}
      \resumeItem{Analyzed tree-based model limits in capturing long-term trends, prompting advanced ML exploration.}
  \resumeItemListEnd

  \resumeProjectHeading
  {\textbf{Financely}
  \href{https://github.com/obro79/financely}{\underline{Github}}$|$\href{https://financely-nine.vercel.app/sign-in}{\underline{Live Demo}}$|$\emph{Node.js, Next.js, React, Tailwind CSS}}{}
  \resumeItemListStart
    \resumeItem{Configured Vercel \textbf{CI/CD} pipeline to auto-build/test/deploy, cutting manual steps 75\%.}
    \resumeItem{Built ETL services in Python/Node to load transactions into SQL, boosting reporting speed 40\%.}
    \resumeItem{Implemented Cypress tests, ensuring \textbf{100\%} sandbox pass with zero integration failures.}
  \resumeItemListEnd

  \resumeProjectHeading
  {\textbf{Option Pricing \& Portfolio Management Web App} \href{https://github.com/obro79/optionStrategyApp}{\underline{Github}}$|$ \emph{Python, NumPy, Pandas, Matplotlib}}{}
  \resumeItemListStart
    \resumeItem{Implemented Black-Scholes and Monte Carlo models; accelerated pricing loops by 4x.}
    \resumeItem{Achieved 98\% PyTest coverage; CI on Linux verifies every commit before merge.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

\end{document}
