\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\pagenumbering{gobble}

\begin{document}

\noindent
\textbf{Owen Fisher} \\
\href{mailto:OwenFisher46@gmail.com}{OwenFisher46@gmail.com} \\
778 700 5680 \\
Vancouver, BC \\
\emph{Available Aug.\ 15–Sep.\ 30, 2025 (part-time, remote)} \\

\vspace{1em}

\noindent
July 22, 2025 \\
Jason H. M. Wong \& Firas Moosvi \\
PrairieLearn Exam Experience Grant Project \\
Department of Computer Science, UBC \\
Vancouver, BC \\

\vspace{1em}

\noindent
\textbf{Re: Part-time Developer (PrairieLearn Exam Experience Project)} \\

\vspace{1em}

Dear Dr. Wong and Dr. Moosvi,

As a third-year Mathematics student with a Computer Science minor at UBC, I am excited to apply for the part-time developer position in your grant-funded project. With my strong foundation in programming languages such as Python, JavaScript/TypeScript, and experience with collaborative review workflows, I am confident that I can make significant contributions to improving the PrairieLearn exam experience.

The emphasis on increasing grading granularity and reducing test anxiety aligns perfectly with my passion for building student-centered tools and clear feedback interfaces. Throughout my projects, including “Financely,” “PrepMe,” and “Pantry Pal,” I have demonstrated my ability to implement features end-to-end, participate in code review, and document decisions transparently.

I am particularly drawn to this opportunity because it allows me to join a remote team that values open communication and collaboration. With experience using feature branches and pull requests to manage reviews, I am comfortable working with distributed teams and contributing to projects remotely. My GitHub profile (\href{https://github.com/obro79}{github.com/obro79}) showcases my ability to learn quickly, iterate fast, and maintain high-quality code.

I am excited about the prospect of joining your team and contributing to the project's success. I can start on or before August 15 and commit the ~90 project hours through September 30. Thank you for considering my application. I would welcome the chance to discuss how I can help deliver clearer, less stressful grade insights to PrairieLearn students.

\vspace{1em}

Sincerely,\\
\textbf{Owen Fisher}

\end{document}